---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# poisrrr

The package poisrrr implements the Poisson Reduced Rank method introduced in [C. Jentsch, E. R. Lee and E. Mammen (2020) Time-dependent Poisson reduced rank models for political text data analysis. Computational Statistics and Data Analysis, 142, 106813](https://doi.org/10.1016/j.csda.2019.106813). See also [C. Jentsch, E. Mammen and E. R. Lee (2021) Poisson reduced rank models with an application to political text data. Biometrika, 108, 2, 455 - 468](https://doi.org/10.1093/biomet/asaa063)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("chroetz/poisrrr")
```
## Example

Create a Term-Document-Matrix form quanteda's inaugural address corpus.

```{r}
library(tidyverse)
quanteda::data_corpus_inaugural %>% 
  quanteda::tokens(remove_punct = TRUE, remove_symbols = TRUE, remove_numbers = TRUE) %>% 
  quanteda::dfm(verbose = FALSE) %>% 
  as.matrix() %>% 
  t() ->
  tdm
tdm <- tdm[rowSums(tdm) > 5, ] # remove rare words
```


Apply the method in for Dimension 2 and plot the resulting plane of documents.

```{r}
library(poisrrr)
K <- 2
theta <- estim(tdm, K, verbose=FALSE)
lst <- theta2plist(theta, K)
v <- lst$v
plot(NA, xlim=c(-0.2, 0.22), ylim=c(-0.3, 0.25), xlab="Dimension 1", ylab="Dimension 2")
points(v)
lines(v)
text(v, labels=rownames(v), cex=0.8, pos=3, offset=0.2)
```


